A thesis draft

### 2018-11-27 res/sections/10-ProjectAnalysis.tex
Minor fix

@@

\vspace{0.5cm}

@@

Another fundamental component in the architecture is the MANO, that has to 
manage the Network Services and the deployment of new VNFs. In coordination 
with Kubernetes, it composes the core of the test-bed architecture. Initially 
identified with Openbaton (the component is described later 
in~\ref{chap:prjan:sec:tech:sub:other:sub:openbaton}), afterword it has been 
discovered to be not flexible enough to support other kinds of virtualization 
techniques than pure or in-cloud virtual machines\todo{Rewrite this}. 
Since this was a strong project requisite that could not be easily changed, it 
has been decided to opt for the creation of a smaller and simpler clone that 
offered a full integration with Docker and Kubernetes.

@@

\subsubsection{Docker-compose} 
Docker-compose is a tool that allows services orchestration. It automates most 
of the tasks that should be performed by hand when launching one or multiple 
docker containers. It's particularly useful when more containers have to 
interact 
together, because\todo{Write down docker-compose functionalities and describe 
the product a little bit} all the services rules are described in a simple 
YAML file. With the birth of Docker Swarm, work has started to port this tool 
to 
the Swarm framework. At the time of this writing, the procedure to port a 
Docker-compose configuration in Docker Swarm (which a description of the 
product can be found in 
sub-section~\ref{chap:prjan:sec:tech:sub:other:sub:swarm}) is still not 
completely transparent, and it requires a sort of compilation, where 
Docker-compose bundles all the necessaries resources into a binary file that 
Docker Swarm will use to allocate the necessary resources.

@@

\subsubsection{Docker Swarm}
\label{chap:prjan:sec:tech:sub:other:sub:swarm}
Introduced in 2014~\cite{swarmGit}, Docker Swarm allows multiple Docker nodes to
cluster together and be seen as one logical unit. This layer completely makes
the underlying infrastructure transparent: data management, as network one, are
totally managed by Docker. Recently, Docker-compose support has been introduced,
making this one-node tool available for clustered systems. At the end of the
day, on one hand Docker Swarm provides an easy way to set up a cluster system
with all the tools configured out-of-the-box, without the necessity to set
networking configurations or installing ad-hoc storage solutions. On the other
hand, though, it doesn't have all the customization options that Kubernetes
offers, thus making the product less flexible. This fundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs.

\subsubsection{OpenVSwitch}
Started in 2009~\cite{ovsGit}, the OpenVSwitch project aims to create an
open-source multi-layer virtual switch. It provides a switching stack for
hardware virtualization environments, implementing several interfaces and
protocols. It has also the possibility to run through Hypervisor virtualization
but it can run under Docker too~\cite{ovsDocker}. OpenVSwitch can route packets
from incoming connections following rules, that can be ``pushed'' in its routing
table from software defined as \textit{controllers}. Additionally, it supports
the OpenFlow communication protocol, in order to set previously cited routing
definitions.

>>>>

\section{Available technologies in the market} \todo{Add images}
\label{chap:prjan:sec:tech}
Before starting any effective work on the project it has been decided to 
perform an analysis of the possible technologies available in the market, 
performing a choice between them and exploiting their possible ``weak 
points''. Proceeding with a top-down approach, the frameworks were chosen from 
the one that had the biggest role in the test-bed to conclude with the 
less-important components.
\subsection{VIM}
A critical component, as the MANO one, is the VIM. Without it, network 
resources can't be managed, and since our project was focused on dynamically 
allocating containerized applications on cloud platforms, we decided to start 
analyzing the right framework for this component first.

@@

% \vspace{0.5cm}

@@

Another fundamental component in the architecture is the MANO, that has to
manage the Network Services and the deployment of new VNFs. Initially identified
with Openbaton (the component is described later
in~\ref{chap:prjan:sec:tech:sub:other:sub:openbaton}), afterword it has been
discovered to be not flexible enough to support other kinds of virtualization
techniques than pure or in-cloud virtual machines. Since this was a strong
project requisite that could not be easily changed, it has been decided to opt
for the creation of a smaller and simpler clone that offered a full integration
with Docker and Kubernetes.

@@

\subsubsection{Docker-compose} 
Docker-compose is a tool that allows services orchestration. It automates most
of the tasks that should be performed by hand when launching one or multiple
docker containers. It's particularly useful when more containers have to
interact together, because all the services rules are described in a simple YAML
file. On top of that, it is possible to restart/stop/destroy selected services,
while keeping the other up. Additionally, it supports containers scaling and it
offers the possibility to simply get logs, interact of inspect with the defined
services. With the birth of Docker Swarm, work has started to port this tool to
the Swarm framework. At the time of this writing, the procedure to port a
Docker-compose configuration in Docker Swarm (which a description of the product
can be found in sub-section~\ref{chap:prjan:sec:tech:sub:other:sub:swarm}) it
has become completely transparent, bundling all the necessaries resources.

@@

\subsubsection{Docker Swarm}
\label{chap:prjan:sec:tech:sub:other:sub:swarm}
Introduced in 2014~\cite{swarmGit}, Docker Swarm allows multiple Docker nodes to
cluster together and be seen as one logical unit. This layer completely makes
the underlying infrastructure transparent: data management, as network one, are
totally managed by Docker. Recently, Docker-compose support has been introduced,
making this one-node tool available for clustered systems. At the end of the
day, on one hand Docker Swarm provides an easy way to set up a cluster system
with all the tools configured out-of-the-box, without the necessity to set
networking configurations or installing ad-hoc storage solutions. On the other
hand, though, it does not have all the customization options that Kubernetes
offers, thus making the product less flexible. This fundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs.

\subsubsection{OpenVSwitch}
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{ovs}
  \caption[OpenVSwitch logo]{OpenVSwitch logo}
\end{figure}
Started in 2009~\cite{ovsGit}, the OpenVSwitch project aims to create an
open-source multi-layer virtual switch. It provides a switching stack for
hardware virtualization environments, implementing several interfaces and
protocols. It has also the possibility to run through Hypervisor virtualization
but it can run under Docker too~\cite{ovsDocker}. OpenVSwitch can route packets
from incoming connections following rules, that can be ``pushed'' in its routing
table from software defined as \textit{controllers}. Additionally, it supports
the OpenFlow communication protocol, in order to set previously cited routing
definitions.
